---
title: "Topic 3"
author: "Paloma Cartwright"
date: "13/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr) #text analysis in R
library(lubridate) #working with date data
library(pdftools) #read in pdfs
library(tidyverse)
library(tidytext)
library(here)
library(LexisNexisTools) #Nexis Uni data wrangling
library(sentimentr)
library(readr)
```


# Intro to sentiment analysis example

For this introductory example, I selected a text excerpt from the National Book Award winning book, The Overstory by Richard Powers.

The excerpt is in .pdf format, so we’ll need a tool (the pdftools package) to help us deal with that.

```{r}
over <- pdf_text('overstory_exerpt.pdf')
over_df <- data.frame(text = over) %>% #create 1-column df with 'text' variable
  mutate(page = 1:n()) #add a page number variable, 'page'

over_text <- over_df %>%
  filter(page %in% 8:41)%>%
  mutate(text = str_split(text, '\n')) %>% #this splits by page.
  unnest(text) %>%  #this splits by line
  mutate(line = str_to_lower(text)) #and convert to all lower case

```

We’ll start by using the Bing sentiment analysis lexicon.

```{r}
bing_sent <- get_sentiments('bing') #grab the bing sentiment lexicon from tidytext
head(bing_sent, n = 20)
```

We need to unnest the text to the word level so we can label the individual sentiment words. Let’s also remove stop words as standard text cleaning procedure. Note: Not every English word is in the lexicons because many English words are pretty neutral.

```{r}

text_words <- over_text %>% 
  unnest_tokens(output = word, input = text, token = "words")

sent_words <- text_words%>% #break text into individual words
  anti_join(stop_words, by = 'word') %>% #returns only the rows without stop words
  inner_join(bing_sent, by = 'word') #joins and retains only sentiment words

```

Create a sentiment score by counting the number of sentiment words occurring per page. We can center the scores around an offset point equal to the average page sentiment score. This lets us measure the sentiment of a given page relative to the overall sentiment of the book.

```{r}
sent_scores <- sent_words %>%
  count(sentiment, page) %>%
  spread(sentiment, n) %>%
  mutate(raw_score = positive - negative, #single sentiment score per page
         offset = mean(positive - negative), #what is the average sentiment per page?
         offset_score = (positive - negative) - offset) %>% #how does this page's sentiment compare to that of the average page?
  arrange(desc(raw_score))

sent_scores
```

```{r}
ggplot(sent_scores, aes(x = page)) +
  theme_classic() +
  geom_bar(aes(y = raw_score), stat = 'identity', fill = 'slateblue3') +
  geom_bar(aes(y = offset_score), stat = 'identity', fill = 'red4') +
  geom_hline(yintercept = sent_scores$offset[1], linetype = 'dashed', size = .5) +
  coord_flip() +
  theme(axis.title.y = element_blank()) +
  labs(title = 'Sentiment analysis: The Overstory',
       y = 'Sentiment score')
```

### Origin of the NRC lexicon

“These guys selected about 10,000 words from an existing thesaurus… and then created a set of five questions to ask about each word that would reveal the emotions and polarity associated with it. That’s a total of over 50,000 questions.

They then asked these questions to over 2000 people, or Turkers, on Amazon’s Mechanical Turk website, paying 4 cents for each set of properly answered questions.

The result is a comprehensive word-emotion lexicon for over 10,000 words.”

Let’s take a look at the most common sentiment words in the data set


```{r}

nrc_sent <- get_sentiments('nrc') #requires downloading a large dataset via prompt

nrc_fear <- get_sentiments("nrc") %>% 
  filter(sentiment == "fear")

#most common words by sentiment
fear_words <- over_text  %>%
  unnest_tokens(output = word, input = text, token = 'words') %>%
  inner_join(nrc_fear) %>%
  count(word, sort = TRUE)

nrc_word_counts <- text_words %>%
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()


```

Let’s break it out and plot the contributions by particular words different sentiment categories

```{r}
book_sent_counts <- text_words %>%
        group_by(page) %>%
        # mutate(page_num = 1:n(),
        #        index = round(page_num / n(), 2)) %>%
        #unnest_tokens(word, line) %>%
        inner_join(get_sentiments("nrc")) %>%
        group_by(sentiment) %>%
        count(word, sentiment, sort = TRUE) %>%
        ungroup()

book_sent_counts %>%
  group_by(sentiment) %>%
  slice_max(n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "Contribution to sentiment",
       y = NULL)
```

# Introduction to the Nexis Uni data source

```{r}

my_files <- list.files(pattern = ".docx", path = getwd(),
                       full.names = TRUE, recursive = TRUE, ignore.case = TRUE)

dat <- lnt_read(my_files) #Object of class 'LNT output'


meta_df <- dat@meta
articles_df <- dat@articles
paragraphs_df <- dat@paragraphs

dat2 <- data_frame(element_id = seq(1:length(meta_df$Headline)), Date = meta_df$Date, Headline = meta_df$Headline)

#May be of use for assignment: using the full text from the articles
# paragraphs_dat <- data_frame(element_id = paragraphs_df$Art_ID, Text  = paragraphs_df$Paragraph)
# 
# dat3 <- inner_join(dat2,paragraphs_dat, by = "element_id")

```



```{r}
mytext <- get_sentences(dat2$Headline)
sent <- sentiment(mytext)

sent_df <- inner_join(dat2, sent, by = "element_id")

sentiment <- sentiment_by(sent_df$Headline)


sent_df %>%
  arrange(sentiment)

sent_df$polarity <- ifelse(sent_df$sentiment < 0, -1, ifelse(sent_df$sentiment > 0, 1, 0))
```


# Pseudocode for the Froelich et al. paper 

mean sentiment by day, summarize 

plot = 

```{r}

```



```{r}

custom_stop_words <- bind_rows(tibble(word = c("your_word"),  
                                      lexicon = c("custom")), 
                               stop_words)
```








